Static Analysis of Tail Behaviour with a \\ Generalized Gamma Algebra

### 2022-08-23 hta/neurips_2022.tex
Initial Overleaf Import

@@

>>>>

\documentclass{article}
\csname remappendix\endcsname

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2022

% ready for submission
\usepackage{neurips_2022}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2022}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2022}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2022}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{array}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{hhline}
\usepackage{multirow}

\usepackage{amsmath}
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\usepackage{todonotes}
\title{Static Analysis of Tail Behaviour with a \\ Generalized Gamma Algebra}

\newcommand{\feynman}[1]{\todo{(Feynman): #1}}
\newcommand{\dd}{\mathrm{d}}
\usepackage{tikz}
\usetikzlibrary{bayesnet}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{multirow}
\usepackage{siunitx}
\usepackage{etoolbox}
\robustify\bfseries
\usepackage[ruled]{algorithm2e}
\usepackage{float}

\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

\sisetup{detect-all = true}

\begin{document}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifdefined\remappendix
\newpage

\appendix

\section{Additional examples}\label{sec:addtl_eg}

To further illustrate the GGA through example, in this section we work
out explicit GGA computations using distributions
from \cref{tab:dist_list} and operations in \cref{tab:gga_operations}
and recover some common probability identities.

\begin{example}[Chi-squared random variables]
	Let $X_1,\dots,X_k$ be $k$ independent standard normal random variables. The variable $Z = \sum_{i=1}^k X_i^2$ is \emph{chi-squared distributed} with $k$ degrees of freedom. Using the generalized Gamma algebra, we can accurately determine the tail behaviour of this random variable directly from its construction. Recall that each $X_i \equiv (0,1/2,2)$, and by the power operation, $X_i^2 \equiv (-1/2,1/2,1)$. Applying the addition operation $k$ times reveals that $Z \equiv (k/2-1,1/2,1)$ and implies that the density of $Z$ is asymptotically $c x^{k/2-1} e^{-x / 2}$ as $x \to \infty$. In fact, the density of $Z$ is exactly $p_Z(x) = c_k x^{k/2-1} e^{-x/2}$ where $c_k = 2^{-k/2} / \Gamma(k/2)$.
\end{example}

\begin{example}[Products of random variables]
	To demonstrate the efficacy of the multiplication operation in our algebra, we consider the product of two exponential, Gaussian, and reciprocal Gaussian random variables. In \cref{sec:proofs}, we manually prove the following.
	\begin{lemma}
	\label{lem:Products}
		Let $X_1,X_2 \sim \mbox{Exp}(\lambda)$ and $Z_1,Z_2 \sim \mathcal{N}(0,1)$ be independent. The densities of $X_1 X_2$, $Z_1 Z_2$ and $Z = 1/Z_1 \cdot 1/Z_2$ satisfy as $x \to \infty$,
		\[
			p_{X_1 X_2}(x) \sim \frac{\lambda^{3/2}\sqrt{\pi}}{x^{1/4}} e^{-2\lambda \sqrt{x}},\quad p_{Z_1 Z_2}(x) \sim \frac{1}{\sqrt{2\pi x}} e^{-x},\quad
			p_{Z}(x) \sim \frac{1}{\sqrt{2\pi}|z|^{3/2}}e^{-1/|z|}.
		\]
	\end{lemma}
	With ease, our algebra correctly determines that $X_1 X_2 \equiv (-\frac14,2\lambda,\frac12)$, $Z_1 Z_2 \equiv (-\frac12, 1, 1)$ and $Z \equiv (-\frac32,1,-1)$.
	% Recall that the Bessel $K$-function of zeroth order, denoted $K_0$, is given by the Fourier transform $K_0(x) = \frac12 \int_{-\infty}^{\infty} e^{ixt} (1+t^2)^{-1/2} \dd t$. This function behaves as $x \to \infty$ as $K_{0}(x)\sim\sqrt{\frac{\pi}{2x}}e^{-x}$. Let $X_1,X_2 \sim \mathrm{Exp}(\lambda)$ be two independent exponentially distributed variables. The density of the product $Z = X_1 X_2$ is given by 
	% \[
	% p_Z(x) = 2\lambda^{2}K_{0}(2\lambda\sqrt{z})\sim\lambda^{3/2}\sqrt{\pi}z^{-1/4}e^{-2\lambda\sqrt{z}}.
	% \]
	% This tail behaviour can be obtained using our algebra as follows: 
	% The density of
	% \[
	% p_Z(x) = \frac1\pi K_0(|x|) \sim \frac{1}{\sqrt{2\pi x}} e^{-x},\qquad \mbox{as }x \to \infty.
	% \]
\end{example}

\begin{example}[Reciprocal distributions]
	Perhaps the most significant challenge with a tail algebra is correctly identifying the tail behaviour of reciprocal distributions. Here, we test the efficacy of our formulation with known reciprocal distributions.
	\begin{itemize}
		\item \emph{Reciprocal normal:} $X \sim \mathcal{N}(0,1) \equiv (0,1/2,2)$, and $X^{-1} \equiv (-2,1/2,-2)$.
		\item \emph{Inverse exponential:} $X \sim \text{Exp}(\lambda) \equiv (0,\lambda,1)$, and $X^{-1} \equiv (-2,\lambda,-1)$.
		\item \emph{Inverse $t$-distribution:} $X \equiv \mathcal{R}_\nu$, and $X^{-1} \equiv \mathcal{R}_2$.
		\item \emph{Inverse Cauchy:} $X \equiv \mathcal{R}_2$, it is known $X^{-1}$
		      has the same distribution and our theory predicts $X^{-1} \equiv \mathcal{R}_2$.
	\end{itemize}
\end{example}

\begin{example}[Cauchy distribution]
	A simple special case of the Student $T$ distribution is the Cauchy distribution, which arises as the ratio of two standard normal random variables. For $X\sim\mathcal{N}(0,1)$, $X \equiv (0,1/2,2)$ and $X^{-1} \equiv (-2,1/2,-2)$. %The reciprocal of a standard normal random variable $X \equiv (0,1/2,2)$ satisfies $X^{-1} \equiv (-2,1/2,-2)$. 
	Hence, the multiplication operation correctly predicts that the ratio of two standard normal random variables is in $\mathcal{R}_2$.
\end{example}

\begin{example}[Student $T$ distribution]
	Let $X$ be a standard normal random variable, and $V$ a chi-squared random variable with $\nu$ degrees of freedom. The random variable $T = X / \sqrt{V / \nu}$ is \emph{$t$-distributed} with $\nu$ degrees of freedom. Since $V \equiv (\nu/2-1,1/2,1)$, multiplying by the constant $1/\nu$ reveals $V / \nu \equiv (\nu/2-1,1/(2\nu),1)$. Applying the square root operation, $\sqrt{V / \nu} \equiv (\nu-1,1/(2\nu),2)$. To compute the division operation, we first take the reciprocal to find $(V/\nu)^{-1/2} \equiv (-\nu-1,1/(2\nu),-2)$. Finally, since $\rho = -2 < 1$ for this random variable, the multiplication operation with $X \equiv (0,1/2,2)$ yields $T \equiv \mathcal{R}_{\nu+1}$, and so the density of $T$ is asymptotically $c x^{-\nu-1}$ as $x \to \infty$.
	Indeed, the density of $T$ satisfies $p_T(x) = c_\nu (1 + x^2 / \nu)^{-(\nu+1)/2}$ where $c_\nu = \Gamma(\frac{\nu+1}{2})/\Gamma(\frac{\nu}{2}) (\nu\pi)^{-1/2}$, which exhibits the predicted tail behaviour.
\end{example}

\begin{example}{Log-normal distribution}
	Although the log-normal distribution does not lie in $\mathcal{G}$, the existence of log-normal tails arising from the multiplicative central limit theorem is suggested by our algebra. Let $X_1,X_2,\dots$ be independent standard normal random variables and let $Z_k = X_1\cdots X_{2^k}$ for each $k=1,2,\dots$. By the multiplicative central limit theorem, letting $\tau = \exp(\mathbb{E}\log |X_i|) \approx 1.13$, $\left(\frac{X_{1}\cdots X_{n}}{\tau}\right)^{1/\sqrt{n}}$ converges in distribution as $n\to\infty$ to a log-normal random variable $Z$ with density
	\[
		p_Z(x) = \frac{1}{x\sqrt{2\pi}} \exp(-\tfrac12 (\log x)^2).
	\]
	Therefore, the same is true for $V_k = (Z_k / \tau)^{2^{-k/2}}$. Using our algebra, we will attempt to reproduce the tail of this density. Letting $\tilde{Z}_k = X_{2^k} \cdots X_{2^{k+1}}$, we see that $Z_{k+1} = Z_k \tilde{Z}_k$, and $Z_k,\tilde{Z}_k$ are iid. Let $Z_k \equiv (\nu_k, \sigma_k, \rho_k)$, by induction using the multiplication operation, we find that $\nu_{k+1} ~=~\frac{1}{\mu}\left(\frac{2\nu_{k}}{\rho_{k}}-\frac{1}{2}\right)=\nu_{k}-\frac{\rho_{k}}{4}$, $\sigma_{k+1}=\mu\left(\sigma_{k}\rho_{k}\right)^{\frac{2}{\mu\rho_{k}}}=\frac{2}{\rho_{k}}\left(\sigma_{k}\rho_{k}\right)=2\sigma_{k}$, and $\rho_{k+1}=\frac{1}{\mu}=\frac{\rho_{k}}{2}$.
	Since $\rho_0 = 2$, $\sigma_0 = 1/2$, and $\nu_0 = 0$, we find that $\rho_k = 2^{1-k}$ and $\sigma_k = 2^{k-1}$. Furthermore, $\nu_{k+1} = \nu_k - 2^{-k-1}$ and so $\nu_k = -1 + 2^{-k}$. Therefore $Z_k \equiv (-1+2^{-k},2^{k-1},2^{1-k})$, and
	\[
		V_k \equiv (-1+2^{-k/2},2^{k-1}\tau^{-2^{1-k}},2^{1-k/2}),
	\]
	and letting $\epsilon_k = 2^{-k/2}$, the tail behaviour of the density of $V_k$ satisfies
	\begin{align*}
		p_k(x) & \sim c_k x^{-1+\epsilon_{k}}\exp\left(-\frac{\epsilon_{k}^{-2}}{2\tau^{-2\epsilon_{k}^{2}}}x^{2\epsilon_k}\right) \\& \sim c_k x^{-1+\epsilon_{k}}\exp\left(-\frac{1}{2\tau^{-2\epsilon_{k}^{2}}}\left(\frac{x^{\epsilon_{k}}-1}{\epsilon_{k}}\right)^{2}\right) \approx c_k x^{-1}\exp\left(-\frac{1}{2}(\log x)^2\right),
	\end{align*}
	as $x \to \infty$, where the approximation improves as $k$ gets larger. The quality of this approximation is shown in \cref{fig:lognormal}.
\end{example}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.48\textwidth]{figures/LogNormal_Bulk.png}
	\includegraphics[width=0.48\textwidth]{figures/LogNormal_Tail.png}
	\caption{Estimation of the log-normal density by tail algebra applied to $V_k$.}
	\label{fig:lognormal}
\end{figure}

\section{Additional details for experiments}

The targets in \Cref{tab:de} and \Cref{tab:vi} are analyzed using
the GGA in \Cref{sec:addtl_eg}. Note that Inverse Gamma (``IG'') corresponds
to the inverse exponential. We selected closed form targets so that
the Pareto tail index $\alpha$ is known analytically and the quality
of theoretical predictions as well as empirical results can be evaluated
against. All experiments are repeated for $100$ trials and $1,000$ samples
from the model (as well as the approximation in VI) were used to compute
each gradient estimate. Losses were trained until convergence, which 
all occurred in under $10,000$ iterations at a $0.05$ learning rate and
the Adam \citep{kingma2014adam} optimizer.

\subsection{Normal target}

Consider the toy example of a Normal target. This case is trivial for
Gaussian based methods and is oftentimes the initialization.
This lack of approximation gap in ADVI is seen in \Cref{fig:normal},
where we also see that GGA achieves similar approximation quality.
This is unsurprising as the GGA approximation in \cref{tab:dist_list}
is also a Normal distribution.

\begin{figure}[H]
	\centering
	\includegraphics[width=.6\textwidth]{figures/de_normal_sum.png}
	\includegraphics[width=.6\textwidth]{figures/vi_normal_sum.png}
	\caption{Density estimation and VI against a known normal target}
	\label{fig:normal}
\end{figure}

\subsection{Chi-square}

Now let $X_{ij} \sim N(0,1)$ and consider $tr X^\top X$.
Such quantities arise in the analysis of random projections.
It is important here to recognize that the power operation $X \mapsto X^2$ is not equivalent to the multiplication operation $X \mapsto X \otimes X$, as multiplication assumes independence.
\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/jl-chi2.png}
	\caption{$5000$ samples of JL matrix trace (blue) vs GGA prediction (yellow)}
	\label{fig:jl_chi2}
\end{figure}

\section{Operations in the Generalized Gamma Algebra}

Whereas \cref{tab:gga_operations} provides a summary of our theory useful
for referencing, in this section we provide additional explanation and references
for how operations on random variables affect their GGA tails.

\paragraph{Ordering.} A total ordering is imposed on the equivalence classes of $\mathcal{G}$ according to the heaviness of tails. In particular, we say that $(\nu_1,\sigma_1,\rho_1) \leq (\nu_2,\sigma_2,\rho_2)$ if $(x^{\nu_1} e^{-\sigma_1 x^{\rho_1}}) / (x^{\nu_2} e^{-\sigma_2 x^{\rho_2}})$ is bounded as $x \to \infty$. As usual, we say $(\nu_1,\sigma_1,\rho_1) < (\nu_2,\sigma_2,\rho_2)$ if $(\nu_1,\sigma_1,\rho_1) \leq (\nu_2,\sigma_2,\rho_2)$ but $(\nu_1,\sigma_1,\rho_1) \not\equiv (\nu_2,\sigma_2,\rho_2)$.

%\paragraph{Multiplication by a Constant.}

\paragraph{Addition.} Tails of this form are  closed under addition. Combining subexponentiality for $\rho < 1$
%Any random variable $X$ in $(\nu,\sigma,\rho)$ for $\rho < 1$ is subexponential 
\cite[Chapter X.1]{asmussen2010ruin}, 
%that is, any sum of iid copies of $X$ asymptotically saturates the union bound: $\mathbb{P}\left(\sum_{i=1}^{n}X_{i}>x\right)\sim\sum_{i=1}^{n}\mathbb{P}(X_{i}>x)$ as $x \to \infty$. Combining this
with \cite[Thm 3.1 \& eqn. (8.3)]{asmussen2017tail},
\begin{proposition}
\label{prop:gga_add}
Denoting the addition of random variables (additive convolution of densities) by $\oplus$,
\begin{multline}
(\nu_{1},\sigma_{1},\rho_{1})\oplus(\nu_{2},\sigma_{2},\rho_{2})
\\\equiv \begin{cases}
\max\{(\nu_{1},\sigma_{1},\rho_{1}),(\nu_{2},\sigma_{2},\rho_{2})\} & \text{ if }\rho_{1}\neq\rho_{2}\text{ or }\rho_{1},\rho_{2}<1\\
\left(\nu_{1}+\nu_{2}+1,\min\{\sigma_{1},\sigma_{2}\},1\right) & \text{ if }\rho_{1}=\rho_{2}=1\\
(\nu_{1}+\nu_{2}+1-\frac{\rho}{2},(\sigma_{1}^{-\frac{1}{\rho-1}}+\sigma_{2}^{-\frac{1}{\rho-1}})^{1-\rho},\rho) & \text{ if }\rho=\rho_{1}=\rho_{2}>1.
\end{cases}
\end{multline}
\end{proposition}

\paragraph{Powers.} For all exponents $\beta > 0$, by invoking a change of variables $x \mapsto x^\beta$, it is easy to show that
%\begin{equation}
%\label{eq:PowerEqn}
$(\nu, \sigma, \rho)^\beta \equiv  \left(\frac{\nu+1}{\beta}-1, \sigma, \frac{\rho}\beta\right).$
%\end{equation}
%\paragraph{Reciprocals.}
We \emph{define} negative powers and reciprocals equivalently to positive powers in the case $\beta < 0$. This equivalence cannot be proven to hold in general since we cannot determine tail asymptotics of the reciprocal without knowledge of its behaviour around zero. Therefore, we implicitly assume that the behaviour around zero mimics the tail behaviour, that is, \cref{eq:GenGammaTails} holds as $x \to 0^+$. However, this can only hold provided $(\nu + 1)/\rho > 0$ and $\rho \neq 0$. In all other cases, including $\mathcal{R}_\nu$, we assume that the density of $X$ approaches a nonzero value near zero, and define the reciprocal to be $\mathcal{R}_{2}$. %By assuming $p_X(x) \to \tilde{c} x^\nu e^{-\sigma x^\rho}$ as $x \to 0^+$, then \cref{eq:PowerEqn} also holds for $\beta < 0$.

\paragraph{Multiplication.}
For any $c \in \mathbb{R} \backslash \{0\}$, it can be readily seen from a change of variables $x \mapsto c x$ that $c (\nu, \sigma, \rho) = (\nu, \sigma / |c|^\rho, \rho)$. The class $\mathcal{G}$ is also closed under multiplication (assuming independence of random variables), as we show in the following result --- the proof is delayed to Appendix C.
\begin{proposition}
\label{prop:Mult}
Denoting the multiplication of independent random variables (multiplicative convolution) by $\otimes$,
\[
(\nu_{1},\sigma_{1},\rho_{1})\otimes(\nu_{2},\sigma_{2},\rho_{2})
\equiv\begin{cases}
\left(\frac{1}{\mu}\left(\frac{\nu_{1}}{|\rho_{1}|}+\frac{\nu_{2}}{|\rho_{2}|}+\frac{1}{2}\right),\sigma,-\frac{1}{\mu}\right) & \text{ if }\rho_{1},\rho_{2}<0\\
\left(\frac{1}{\mu}\left(\frac{\nu_{1}}{\rho_{1}}+\frac{\nu_{2}}{\rho_{2}}-\frac{1}{2}\right),\sigma,\frac{1}{\mu}\right) & \text{ if }\rho_{1},\rho_{2}>0\\
\mathcal{R}_{|\nu_1|} & \mbox{ if }\rho_{1}\leq0,\rho_{2}>0 \\
\mathcal{R}_{\min\{|\nu_1|,|\nu_2|\}} & \mbox{ if }\rho_{1}=0,\rho_{2}=0
\end{cases}
\]
where $\mu=\frac{1}{|\rho_{1}|}+\frac{1}{|\rho_{2}|}=\frac{|\rho_{1}|+|\rho_{2}|}{|\rho_{1}\rho_{2}|}$ and $\sigma=\mu(\sigma_{1}|\rho_{1}|)^{\frac{1}{\mu|\rho_{1}|}}(\sigma_{2}|\rho_{2}|)^{\frac{1}{\mu|\rho_{2}|}}$. 
\end{proposition}
% \begin{proof}
% Appendix C.
% \end{proof}

%\feynman{I added this back; we need it for the StudentT example but this result currently doesn't give what we need}
%The next binary operation of interest is \emph{multiplication}. Using Cauchy's inequality, we can adopt the naive
%\[
%X \cdot Y \equiv \max\{X^2, Y^2\}.
%\]
%In the case where $X,Y \in \mathcal{E}$, this turns out to be reasonable. However, for any other use case, Breiman's lemma suggests that $X \cdot Y \equiv \max\{X, Y\}$. \todo{Perform Tauberian analysis to determine sharpness of these operations}.

\paragraph{Product of Densities.}

We can also consider a product of densities operation acting on two random variables $X,Y$, denoted $X \& Y$, by
$p_{X \& Y}(x) = c p_X(x) p_Y(x)$,
where $c > 0$ is an appropriate normalizing constant and $p_X,p_Y,p_{X\& Y}$ are the densities of $X$, $Y$, and $X \& Y$, respectively. In terms of the equivalence classes:
\[
(\nu_1,\sigma_1,\rho_1)\&(\nu_2,\sigma_2,\rho_2) 
\equiv \begin{cases}
(\nu_{1}+\nu_{2},\sigma_{1},\rho_{1}) & \text{ if }\rho_{1}<\rho_{2}\\
(\nu_{1}+\nu_{2},\sigma_{1}+\sigma_{2},\rho) & \text{ if }\rho=\rho_{1}=\rho_{2}\\
(\nu_{1}+\nu_{2},\sigma_{2},\rho_{2}) & \text{ otherwise.}
\end{cases}
\]
Note that this particular operation does not require either $p_X$ or $p_Y$ to be normalized --- only the tail behaviour is needed. We may also use this to work out the tail behaviour of a posterior density, provided the tail behaviour of the likelihood in the parameters is known.

\paragraph{Lipschitz Functions.}

There are many multivariate functions that cannot be readily represented in terms of the operations covered thus far. For these, it is important to specify the tail behaviour of pushforward measures under Lipschitz-continuous functions. Fortunately, this is covered by \cref{lem:lipschitz} below, presented in \cite[Proposition 1.3]{ledoux2001concentration}. 
H\"{o}lder-continuous functions can also be represented as a composition of a power operation and a Lipschitz-continuous function. 
\begin{lemma}\label{lem:lipschitz}
For any Lipschitz continuous function $f:\mathbb{R}^d \to \mathbb{R}$ satisfying $\|f(x)-f(y)\|\leq L\|x -y\|$ for $x,y \in \mathbb{R}^d$, there is $f(X_1,\dots,X_d) \equiv L \max\{X_1,\dots,X_d\}.$
\end{lemma}

\paragraph{Power Law Approximation.} Note that as $x \to \infty$, $p_{|X|}(x) \sim c x^\nu e^{-\sigma x^\rho} = \tilde{c}x^\nu e^{-\sigma\rho\frac{x^\rho - 1}{\rho}} \approx \tilde{c} x^\nu e^{-\sigma\rho \log x}$
    \[
    p_{|X|}(x) \sim c x^\nu e^{-\sigma x^\rho} = \tilde{c} x^\nu e^{-\sigma(x^\rho - 0)} = \tilde{c} x^\nu e^{-\sigma\rho\frac{x^\rho - 1}{\rho}} \approx \tilde{c} x^\nu e^{-\sigma\rho \log x} = \tilde{c} x^{\nu-\sigma \rho},
    \]
    where we have used the approximation $\log x = \rho^{-2}(x^\rho - 1) + \mathcal{O}(\rho^2)$. Consequently, we can represent tails of this form by the Student $t$ distribution with $|\nu-\sigma\rho|-1$ degrees of freedom. In practice, we find this approximation tends to \emph{overestimate} the heaviness of the tail. Alternatively, the generalized Gamma density (\ref{eq:GenGammaDensity}) satisfies $\mathbb{E}X^r = \sigma^{-r/\rho} \Gamma(\frac{\nu+1+r}{\rho})/\Gamma(\frac{\nu+1}{\rho})$ for $r > 0$. Let $\alpha > 0$ be such that $\mathbb{E}X^\alpha = 2$. By Markov's inequality, the tail of $X$ satisfies $\mathbb{P}(X>x)\leq 2 x^{-\alpha}$. Therefore, we can represent tails of this form by the Student $t$ distribution with $\alpha+1$ degrees of freedom (generate $X \sim t_{\alpha}$). In practice, we find this approximation to be more accurate, and is hence used in Section 4.1.

\section{List of univariate distributions}

\bgroup
\def\arraystretch{2}
\begin{longtable}{|c|c|c|c|}
\caption{List of univariate distributions}\label{tab:dist_list}\\
\hline 
Name & Support & Density $p(x)$ & Class\tabularnewline
\hline 
\hline 
Benktander Type II & $(0,\infty)$ & $e^{\frac{a}{b}(1-x^{b})}x^{b-2}(ax^{b}-b+1)$ & $(2b-2,\frac{a}{b},b)$\tabularnewline
\hline 
Beta prime distribution & $(0,\infty)$ & $\frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)}x^{\alpha-1}(1+x)^{-\alpha-\beta}$ & $\mathcal{R}_{\beta+1}$\tabularnewline
\hline 
Burr distribution & $(0,\infty)$ & $ckx^{c-1} (1+x^{c})^{-k-1}$ & $\mathcal{R}_{ck+1}$\tabularnewline
\hline 
Cauchy distribution & $(-\infty,\infty)$ & $(\pi\gamma)^{-1}\left[1+\left(\frac{x-x_{0}}{\gamma}\right)^{2}\right]^{-1}$ & $\mathcal{R}_{2}$\tabularnewline
\hline 
Chi distribution & $(0,\infty)$ & $\frac{1}{2^{k/2-1}\Gamma(k/2)}x^{k-1}e^{-x^{2}/2}$ & $(k-1,\frac{1}{2},2)$\tabularnewline
\hline 
Chi-squared distribution & $(0,\infty)$ & $\frac{1}{2^{k/2}\Gamma(k/2)}x^{\frac{k}{2}-1}e^{-x/2}$ & $(\frac{k}{2}-1,\frac{1}{2},1)$\tabularnewline
\hline 
Dagum distribution & $(0,\infty)$ & $\frac{ap}{x}\left(\frac{x}{b}\right)^{ap}\left(\left(\frac{x}{b}\right)^{a}+1\right)^{-p-1}$ & $\mathcal{R}_{a+1}$\tabularnewline
\hline 
Davis distribution & $(0,\infty)$ & $\propto(x-\mu)^{-1-n}/\left(e^{\frac{b}{x-\mu}}-1\right)$ & $(-1-n,b,-1)$\tabularnewline
\hline 
Exponential distribution & $(0,\infty)$ & $\lambda e^{-\lambda x}$ & $(0,\lambda,1)$\tabularnewline
\hline 
$F$ distribution & $(0,\infty)$ & $\propto x^{d_{1}/2-1}(d_{1}x+d_{2})^{-(d_{1}+d_{2})/2}$ & $\mathcal{R}_{d_{2}/2+1}$\tabularnewline
\hline 
Fisher $z$-distribution & $(-\infty,\infty)$ & $\propto\frac{e^{d_{1}x}}{(d_{1}e^{2x}+d_{2})^{(d_{1}+d_{2})/2}}$ & $(0,d_{2},1)$\tabularnewline
\hline 
Frechet distribution & $(0,\infty)$ & $\frac{\alpha}{\lambda}\left(\frac{x-m}{\lambda}\right)^{-1-\alpha}e^{-\left(\frac{x-m}{\lambda}\right)^{-\alpha}}$ & $(-1-\alpha,\lambda^{\alpha},-\alpha)$\tabularnewline
\hline 
Gamma distribution & $(0,\infty)$ & $\frac{\beta^{\alpha}}{\Gamma(\alpha)}x^{\alpha-1}e^{-\beta x}$ & $(\alpha-1,\beta,1)$\tabularnewline
\hline 
Gamma/Gompertz distribution & $(0,\infty)$ & $bse^{bx}\beta^{s}/(\beta-1+e^{bx})^{s+1}$ & $(0,bs,1)$\tabularnewline
\hline 
Generalized hyperbolic distribution & $(-\infty,\infty)$ & $\propto e^{\beta(x-\mu)}\frac{K_{\lambda-1/2}(\alpha\sqrt{\delta^{2}+(x-\mu)^{2}})}{(\delta^{2}+(x-\mu)^{2})^{1/4-\lambda/2}}$ & $(\lambda-1,\alpha-\beta,1)$\tabularnewline
\hline 
Generalized Normal distribution & $(-\infty,\infty)$ & $\frac{\beta}{2\alpha\Gamma(1/\beta)}\exp\left(-\left(\frac{|x-\mu|}{\alpha}\right)^{\beta}\right)$ & $(0,\alpha^{-\beta},\beta)$\tabularnewline
\hline 
Geometric stable distribution & $(-\infty,\infty)$ & no closed form & $\mathcal{R}_{\alpha+1}$\tabularnewline
\hline 
Gompertz distribution & $(0,\infty)$ & $\sigma \eta \exp(\eta + \sigma x - \eta e^{\sigma x})$ & $\mathcal{L}$\tabularnewline
\hline
Gumbel distribution & $(0,\infty)$ & $\beta^{-1} e^{-(\beta^{-1}(x-\mu)+e^{-\beta^{-1}(x-\mu)})}$ & $(0,\frac{1}{\beta},1)$\tabularnewline
\hline
Gumbel Type II distribution & $(0,\infty)$ & $\alpha\beta x^{-\alpha-1}e^{-\beta x^{-\alpha}}$ & $(-\alpha-1,\beta,-\alpha)$\tabularnewline
\hline 
Holtsmark distribution & $(-\infty,\infty)$ & no closed form & $\mathcal{R}_{5/2}$\tabularnewline
\hline 
Hyperbolic secant distribution & $(-\infty,\infty)$ & $\frac{1}{2}\text{sech}\left(\frac{\pi x}{2}\right)$ & $(0,\frac{\pi}{2},1)$\tabularnewline
\hline 
Inverse chi-squared distribution & $(0,\infty)$ & $\frac{2^{-k/2}}{\Gamma(k/2)}x^{-k/2-1}e^{-1/(2x)}$ & $(-\frac{k}{2}-1,\frac{1}{2},-1)$\tabularnewline
\hline 
Inverse gamma distribution & $(0,\infty)$ & $\frac{\beta^{\alpha}}{\Gamma(\alpha)}x^{-\alpha-1}e^{-\beta/x}$ & $(-\alpha-1,\beta,-1)$\tabularnewline
\hline 
Levy distribution & $(0,\infty)$ & $\sqrt{\frac{c}{2\pi}}(x-\mu)^{-3/2}e^{-\frac{c}{2(x-\mu)}}$ & $(-\frac{3}{2},\frac{c}{2},-1)$\tabularnewline
\hline 
Laplace distribution & $(-\infty,\infty)$ & $\frac{1}{2\lambda}\exp\left(-\frac{|x-\mu|}{\lambda}\right)$ & $(0,\frac{1}{\lambda},1)$\tabularnewline
\hline 
Logistic distribution & $(-\infty,\infty)$ & $\frac{e^{-(x-\mu)/\lambda}}{\lambda(1+e^{-(x-\mu)/\lambda})^{2}}$ & $(0,\frac{1}{\lambda},1)$\tabularnewline
\hline 
Log-Cauchy distribution &
$(0,\infty)$ & $\frac{\sigma}{x\pi}((\log x - \mu)^2 + \sigma^2)^{-1}$ & $\mathcal{R}_1$\tabularnewline
\hline
Log-Laplace distribution & $(0,\infty)$ & $\frac{1}{2\lambda x}\exp\left(-\frac{\left|\log x-\mu\right|}{\lambda}\right)$ & $\mathcal{R}_{1/\lambda+1}$\tabularnewline
\hline 
Log-logistic distribution & $(0,\infty)$ & $\frac{\beta}{\alpha}\left(\frac{x}{\alpha}\right)^{\beta-1}\left(1+\left(\frac{x}{\alpha}\right)^{\beta}\right)^{-2}$ & $\mathcal{R}_{\beta+1}$\tabularnewline
\hline
Log-$t$ distribution &
$(0,\infty)$ &
$\propto x^{-1} (1 + \frac1{\nu}(\log x - \mu)^2)^{-\frac{\nu+1}{2}}$ & $\mathcal{R}_1$\tabularnewline
\hline 
Lomax distribution & $(0,\infty)$ & $\frac{\alpha}{\lambda}\left(1+\frac{x}{\lambda}\right)^{-\alpha-1}$ & $\mathcal{R}_{\alpha+1}$\tabularnewline
\hline 
Maxwell-Boltzmann distribution & $(0,\infty)$ & $\sqrt{\frac{2}{\pi}}\frac{x^{2}e^{-x^{2}/(2\sigma^{2})}}{\sigma^{3}}$ & $(2,\frac{1}{2\sigma^{2}},2)$\tabularnewline
\hline 
Normal distribution & $(-\infty,\infty)$ & $\frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^{2}}$ & $(0,\frac{1}{2\sigma^{2}},2$)\tabularnewline
\hline 
Pareto distribution & $(x_{0},\infty)$ & $\alpha x_{0}^{\alpha}x^{-\alpha-1}$ & $\mathcal{R}_{\alpha+1}$\tabularnewline
\hline 
Rayleigh distribution & $(0,\infty)$ & $\frac{x}{\sigma^{2}}e^{-x^{2}/(2\sigma^{2})}$ & $(1,\frac{1}{2\sigma^{2}},2)$\tabularnewline
\hline 
Rice distribution & $(0,\infty)$ & $\frac{x}{\sigma^{2}}\exp\left(-\frac{(x^{2}+\nu^{2})}{2\sigma^{2}}\right)I_{0}\left(\frac{x\nu}{\sigma^{2}}\right)$ & $(\frac{1}{2},\frac{1}{2\sigma^{2}},2)$\tabularnewline
\hline 
Skew normal distribution & $(-\infty,\infty)$ & no closed form & $(0,\frac{1}{2\sigma^{2}},2)$\tabularnewline
\hline 
Slash distribution & $(-\infty,\infty)$ & $\frac{1-e^{-\frac{1}{2}x^{2}}}{\sqrt{2\pi}x^{2}}$ & $(-2,\frac{1}{2},2)$\tabularnewline
\hline 
Stable distribution & $(-\infty,\infty)$ & no closed form & $\mathcal{R}_{\alpha+1}$\tabularnewline
\hline 
